### 2022-02-22 New-Manuscript/sections/adp_model.tex
added more "full" scenarios

\begin{equation}\begin{alignedat}{10}
		&	v(S') = \Bigg( 
		&& 	\beta^0 + 
		\bigg( \sum_{p \in p\_co} \beta_{p}^{ul} (\hat{ul_{p}}) \bigg) +
			\bigg( \sum_{dc} \beta_{0dkc}^{pw} pea_{dkc} \bigg) +
			\bigg( \sum_{m=1,dkc}^{TL_{c}-1} \beta_{mdkc}^{pw} 
				(\hat{pw}_{m-1dkc} \bigg) + \\
		&	&&	\qquad \qquad \bigg( \sum_{m=TL_{c}dkc}^{M-1} \beta_{mdkc}^{pw} 
		(	\hat{pw}_{m-1dkc} + E[pwt\_d_{m-1d-1c}] - E[pwt\_d_{d}] 
			+ E[pwt\_k_{k-1}] - E[pwt\_k_{k}])\bigg) + \\
		&	&&	\qquad \qquad \bigg( \sum_{dkc} \beta_{Mdkc}^{pw} 
		\sum_{M-1}^{M} ( \hat{pw}_{mdkc} + E[pwt\_d_{md-1c}] - E[pwt\_d_{d}] 
			+ E[pwt\_k_{k-1}] - E[pwt\_k_{k}])\bigg) + \\
		& 	&&	\bigg( \sum_{t=1m=1dkc}^{T-1, TL_{c}-1} \beta_{tmdkc}^{ps} 
				(\hat{ps}_{t+1m-1dkc}) \bigg) + \\
		&	&&	\qquad \bigg( \sum_{t=1m=TL_{c}dkc}^{T-1M-1} \beta_{tmdkc}^{ps} 
				(\hat{ps}_{t+1m-1dkc} + E[pst\_d_{t+1m-1d-1c}] - 
				E[pst\_d_{d}] + E[pst\_k_{k-1}] - E[pst\_k_{k}]) \bigg)  + \\
		&	&&	\qquad \bigg( \sum_{t=1dkc}^{T-1} \beta_{tmdkc}^{ps} \sum_{M-1}^{M}
				(\hat{ps}_{t+1mdkc} + E[pst\_d_{t+1md-1c}] - 
				E[pst\_d_{d}] + E[pst\_k_{k-1}] - E[pst\_k_{k}]) \bigg) 
		\Bigg)
	\end{alignedat}
\end{equation}

@@

>>>>

\begin{equation}
	\begin{alignedat}{10}
		&	v(S') = \Bigg( 
		&& 	\beta^0 + 
		\bigg( \sum_{p \in p\_co} \beta_{p}^{ul} (\hat{ul_{p}}) \bigg) +
			\bigg( \sum_{dc} \beta_{0dkc}^{pw} pea_{dkc} \bigg) +
			\bigg( \sum_{m=1,dkc}^{TL_{c}-1} \beta_{mdkc}^{pw} 
				(\hat{pw}_{m-1dkc} \bigg) + \\
		&	&&	\qquad \qquad \bigg( \sum_{m=TL_{c}dkc}^{M-1} \beta_{mdkc}^{pw} 
		(	\hat{pw}_{m-1dkc} + E[pwt\_d_{m-1d-1c}] - E[pwt\_d_{d}] 
			+ E[pwt\_k_{k-1}] - E[pwt\_k_{k}])\bigg) + \\
		&	&&	\qquad \qquad \bigg( \sum_{dkc} \beta_{Mdkc}^{pw} 
		\sum_{M-1}^{M} ( \hat{pw}_{mdkc} + E[pwt\_d_{md-1c}] - E[pwt\_d_{d}] 
			+ E[pwt\_k_{k-1}] - E[pwt\_k_{k}])\bigg) + \\
		& 	&&	\bigg( \sum_{t=1m=1dkc}^{T-1, TL_{c}-1} \beta_{tmdkc}^{ps} 
				(\hat{ps}_{t+1m-1dkc}) \bigg) + \\
		&	&&	\qquad \bigg( \sum_{t=1m=TL_{c}dkc}^{T-1M-1} \beta_{tmdkc}^{ps} 
				(\hat{ps}_{t+1m-1dkc} + E[pst\_d_{t+1m-1d-1c}] - 
				E[pst\_d_{d}] + E[pst\_k_{k-1}] - E[pst\_k_{k}]) \bigg)  + \\
		&	&&	\qquad \bigg( \sum_{t=1dkc}^{T-1} \beta_{tmdkc}^{ps} \sum_{M-1}^{M}
				(\hat{ps}_{t+1mdkc} + E[pst\_d_{t+1md-1c}] - 
				E[pst\_d_{d}] + E[pst\_k_{k-1}] - E[pst\_k_{k}]) \bigg) 
		\Bigg)
	\end{alignedat}
\end{equation}

@@

\subsection{Representation in terms of actions only}

\begin{equation}
	\begin{alignedat}{10}
		& \beta_{ul} && \text{if } ul_{p} >0: && sc_{1mdkc} * \beta_{p}^{ul}  && \forall pmdkc \\
		& \beta_{pw} \text{ part 1 } && all && - sc_{tm-1dkc} * \beta_{mdkc}^{pw} && \forall tm\in\{1...M-1\}dkc \\
		& \beta_{pw} \text{ part 1 } && all && - sc_{tM-1dkc} * \beta_{Mdkc}^{pw} && \forall tdkc \\
		& \beta_{pw} \text{ part 1 } && all && - sc_{tMdkc} * \beta_{Mdkc}^{pw} && \forall tdkc \\
		& \beta_{pw} \text{ part 2 } && all && - sc_{tm-1d-1kc} * (\beta_{mdkc}^{pw} * ptp\_dc_{d-1c}) && \forall tdkc, m \in \{TL_{c} ... M-1 \} \\
		& \beta_{pw} \text{ part 2 } && all && - sc_{tM-1d-1kc} * (\beta_{Mdkc}^{pw} * ptp\_dc_{d-1c}) && \forall tdkc \\
		& \beta_{pw} \text{ part 2 } && all && - sc_{tMd-1kc} * (\beta_{Mdkc}^{pw} * ptp\_dc_{d-1c}) && \forall tdkc \\ 
		& \beta_{pw} \text{ part 3 } && all && sc_{tm-1dkc} * (\beta_{mdkc}^{pw} * ptp\_dc_{dc}) && \forall tdkc, m \in \{TL_{c} ... M-1 \} \\
		& \beta_{pw} \text{ part 3 } && all && sc_{tM-1dkc} * (\beta_{Mdkc}^{pw} * ptp\_dc_{dc}) && \forall tdkc \\
		& \beta_{pw} \text{ part 3 } && all && sc_{tMdkc} * (\beta_{Mdkc}^{pw} * ptp\_dc_{dc}) && \forall tdkc \\
		& \beta_{pw} \text{ part 4 } && all && -sc_{tm-1dk-1c} * (\beta_{mdkc}^{pw} * ptp\_kc_{k-1c}) && \forall tdkc, m \in \{ TL_{c} ... M-1 \} \\
		& \beta_{pw} \text{ part 4 } && all && -sc_{tm-1d-1k-1c} * (\beta_{mdkc}^{pw} * ptp\_kc_{k-1c} * ptp\_dc_{d-1c}) && \forall tdkc, m \in \{ TL_{c} ... M-1 \} \\ 
		& \beta_{pw} \text{ part 4 } && all && sc_{tm-1dk-1c} * (\beta_{mdkc}^{pw} * ptp\_kc_{k-1c} * ptp\_dc_{dc}) && \forall tdkc, m \in \{ TL_{c} ... M-1 \} \\
		& \beta_{pw} \text{ part 4 } && all && -sc_{tM-1dk-1c} * (\beta_{Mdkc}^{pw} * ptp\_kc_{k-1c}) && \forall tdkc \\
		& \beta_{pw} \text{ part 4 } && all && -sc_{tM-1d-1k-1c} * (\beta_{Mdkc}^{pw} * ptp\_kc_{k-1c} * ptp\_dc_{d-1c}) && \forall tdkc \\ 
		& \beta_{pw} \text{ part 4 } && all && sc_{tM-1dk-1c} * (\beta_{Mdkc}^{pw} * ptp\_kc_{k-1c} * ptp\_dc_{dc}) && \forall tdkc  \\
		& \beta_{pw} \text{ part 4 } && all && -sc_{tMdk-1c} * (\beta_{Mdkc}^{pw} * ptp\_kc_{k-1c}) && \forall tdkc \\
		& \beta_{pw} \text{ part 4 } && all && -sc_{tMd-1k-1c} * (\beta_{Mdkc}^{pw} * ptp\_kc_{k-1c} * ptp\_dc_{d-1c}) && \forall tdkc \\ 
		& \beta_{pw} \text{ part 4 } && all && sc_{tMdk-1c} * (\beta_{Mdkc}^{pw} * ptp\_kc_{k-1c} * ptp\_dc_{dc}) && \forall tdkc \\
		& \beta_{pw} \text{ part 5 } && all && sc_{tm-1dkc} * (\beta_{mdkc}^{pw} * ptp\_kc_{kc}) && \forall tdkc, m \in \{ TL_{c} ... M-1 \} \\
		& \beta_{pw} \text{ part 5 } && all && sc_{tm-1d-1kc} * (\beta_{mdkc}^{pw} * ptp\_kc_{kc} * ptp\_dc_{d-1c}) && \forall tdkc, m \in \{ TL_{c} ... M-1 \} \\ 
		& \beta_{pw} \text{ part 5 } && all && -sc_{tm-1dkc} * (\beta_{mdkc}^{pw} * ptp\_kc_{kc} * ptp\_dc_{dc}) && \forall tdkc, m \in \{ TL_{c} ... M-1 \} \\
		& \beta_{pw} \text{ part 5 } && all && sc_{tM-1dkc} * (\beta_{Mdkc}^{pw} * ptp\_kc_{kc}) && \forall tdkc \\
		& \beta_{pw} \text{ part 5 } && all && sc_{tM-1d-1kc} * (\beta_{Mdkc}^{pw} * ptp\_kc_{kc} * ptp\_dc_{d-1c}) && \forall tdkc \\ 
		& \beta_{pw} \text{ part 5 } && all && -sc_{tM-1dkc} * (\beta_{Mdkc}^{pw} * ptp\_kc_{kc} * ptp\_dc_{dc}) && \forall tdkc  \\
		& \beta_{pw} \text{ part 5 } && all && sc_{tMdkc} * (\beta_{Mdkc}^{pw} * ptp\_kc_{kc}) && \forall tdkc \\
		& \beta_{pw} \text{ part 5 } && all && sc_{tMd-1kc} * (\beta_{Mdkc}^{pw} * ptp\_kc_{kc} * ptp\_dc_{d-1c}) && \forall tdkc \\ 
		& \beta_{pw} \text{ part 5 } && all && -sc_{tMdkc} * (\beta_{Mdkc}^{pw} * ptp\_kc_{kc} * ptp\_dc_{dc}) && \forall tdkc \\
		& \beta_{ps} \text{ part 1 } && all && sc_{t+1m-1dkc} * \beta_{tmdkc}^{ps} && \forall t \in \{1...T-1 \} m \in \{ 1...M-1 \} dkc \\
		& \beta_{ps} \text{ part 1 } && all && sc_{t+1M-1dkc} * \beta_{tMdkc}^{ps} && \forall t \in \{1...T-1 \} m \in \{ 1...M-1 \} dkc \\
		& \beta_{ps} \text{ part 1 } && all && sc_{t+1Mdkc} * \beta_{tMdkc}^{ps} && \forall t \in \{1...T-1 \} dkc \\
		& \beta_{ps} \text{ part 2 } && all && sc_{t+1m-1d-1kc} * (\beta_{tmdkc}^{ps} * ptp\_dc_{d-1c}) && \forall t \in \{1...T-1 \} dkc, m \in \{TL_{c} ... M-1 \} \\
		& \beta_{ps} \text{ part 2 } && all && sc_{t+1M-1d-1kc} * (\beta_{tMdkc}^{ps} * ptp\_dc_{d-1c}) && \forall t \in \{1...T-1 \} dkc \\
		& \beta_{ps} \text{ part 2 } && all && sc_{t+1Md-1kc} * (\beta_{tMdkc}^{ps} * ptp\_dc_{d-1c}) && \forall t \in \{1...T-1 \} dkc \\ 
	\end{alignedat}
\end{equation}
